\begin{longtable}{|| l l l l ||}%
\hline%
&TM46 — Psywave&x 1&9 days\\%
\multicolumn{4}{||m{\textwidth}||}{At the north extremity of Underground Path.}%
\hline%
&Full Heal&x 1&4 days\\%
\multicolumn{4}{||m{\textwidth}||}{Behind the tree at the start of the eastern path in Underground Path.}%
\hline%
&Max Ether&x 2&11 days\\%
\multicolumn{4}{||m{\textwidth}||}{Behind the southmost tree in Underground Path.}%
\hline%
&Antidote&x 2&7 days\\%
\multicolumn{4}{||m{\textwidth}||}{Behind the eastmost tree in Underground Path.}%
\hline%
&Revive&x 1&3{-}9 days\\%
\multicolumn{4}{||m{\textwidth}||}{In the path west of the stairs in Underground Warehouse.}%
\hline%
&Super Potion&x 1{-}2&4{-}5 days\\%
\multicolumn{4}{||m{\textwidth}||}{At the end of the path west of the stairs in Underground Warehouse.}%
\hline%
&Max Potion&x 1&3{-}8 days\\%
\multicolumn{4}{||m{\textwidth}||}{Between boxes in the southern part of Underground Warehouse.}%
\hline%
&Antidote&x 1&2{-}3 days\\%
\multicolumn{4}{||m{\textwidth}||}{Immediately next to the west exit in Underground Warehouse.}%
\hline%
&Great Ball&x 2{-}5&4{-}7 days\\%
\multicolumn{4}{||m{\textwidth}||}{Hidden Item. In the trash placed in the northwest corner of Underground Warehouse.}%
\hline%
&TM62 — Taunt&x 1&18 days\\%
\multicolumn{4}{||m{\textwidth}||}{In the final room of the lever puzzle in Underground Basement.}%
\hline%
&BrightPowder&x 1&5{-}12 days\\%
\multicolumn{4}{||m{\textwidth}||}{Hidden Item. In the trash can placed in the southeast corner of Underground Basement.}%
\hline%
&Miracle Seed&x 1&10 days\\%
\multicolumn{4}{||m{\textwidth}||}{Hidden Item. In the jar between the two exits of Underground Basement.}%
\hline%
\endhead%
\hline%
\caption{Items in Goldenrod City}%
\label{tab:GoldenrodCityItems}%
\end{longtable}