\begin{longtable}{|| l l l l ||}%
\hline%
&Razor Claw&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{In the south-east corner of 1F.}%
\hline%
&Ultra Ball&x 3&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{In the north-west corner of 1F.}%
\hline%
&Full Heal&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{Near the nothern exit, in front of Trainer Alex in 1F.}%
\hline%
&Max Potion&x 2&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{At the very end of the south-east path in 2F. Requires Rock Smash.}%
\hline%
&Zinc&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{In the south-west corner of 2F. Requires Rock Smash.}%
\hline%
&Max Repel&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{Hidden item. On the wall block adjacent to the rock smash rocks in the south-east corner, north-east from Psychic Bryce in 2F. Requires Rock Smash.}%
\hline%
&Rare Candy&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{Hidden item. On the rock one tile north of the northmost rock smash rock in the south-east path of 2F. Requires Rock Smash.}%
\hline%
&Max Elixir&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{Across the water from Fakuman, in the middle of B1F.}%
\hline%
&Pearl&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{Hidden item. From the south-westmost ladder, on the westmost accessible small rock before going down the stairs in B1F.}%
\hline%
&Calcium&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{Hidden item. On the small rock Black Belt Velskulz is running around near the north-west stairs of B1F.}%
\hline%
&Full Restore&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{In the north-west corner of B1F Deep. Requires Rock Smash.}%
\hline%
&Ether&x 2&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{In the middle of the northern body of water at the end of the south-east path in B1F Deep.}%
\hline%
&HP Up&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{In the west corner of the rock maze in the middle of B1F Deep.}%
\hline%
&Big Pearl&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{Hidden item. After entering the maze part from the south, follow the path north, west, north, east, then go south one tile, on the rock to the east in B1F Deep. Hinted by Mrs. Cherry.}%
\hline%
&Leftovers&x 1&Not respawnable\\%
\multicolumn{4}{||m{\textwidth}||}{Hidden item. After entering the maze part from the center, follow the path north, west one tile, north, west, south, west, north, on the rock to the north in B1F Deep.}%
\hline%
\endhead%
\hline%
\caption{Items in Sinnoh Victory Road 1F}%
\label{tab:SinnohVictoryRoad1FItems}%
\end{longtable}